---
title: "Instrumental Variables Regression"
output: html_document
---

```{r}
library(AER)
library(stargazer)
library(dplyr)
```

## Data
```{r}
data("CigarettesSW")
```

## Model
### A Single Regressor and A Single Instrument
1. 生成人均實質價格和營業稅的變數：
```{r}
# generate 2 variables
CigarettesSW <- CigarettesSW %>%
    mutate(
      Rprice = price/cpi,
      SalesTax = (taxs - tax)/cpi
    )
    
# correlation between SalesTax and price
cor(CigarettesSW$SalesTax, CigarettesSW$price)
```

2. 取出1995年的資料來分析：
```{r}
df1995 <- subset(CigarettesSW, year == 1995)
```

3. 跑 $log(P^{cigarettes}_i)$ 對 $SalesTax$ 回歸
```{r}
# first-stage regression
cig_s1 <- lm(log(Rprice) ~ SalesTax, data = df1995)

coeftest(cig_s1, vcov = vcovHC, type = "HC1")

summary(cig_s1)
```

```{r}
cig_s1
```

4. 存取第一階段回歸，$log(P^{cigarettes}_i)$ 的結果
```{r}
cigp_pred1 <- cig_s1$fitted.values
```

5. 做第二階段，$log(Q^{cigarettes}_i)$ 對 $log(P^{cigarettes}_i)$ 回歸。
```{r}
# solution 1
cig_s2 <- lm(log(df1995$packs) ~ cigp_pred1)

coeftest(cig_s2, vcov = vcovHC, type = "HC1")

# solution 2
cig_ivreg <- ivreg(log(packs) ~ log(Rprice) | SalesTax, data = df1995)

coeftest(cig_ivreg, vcov = vcovHC, type = "HC1")
```

### The General IV Regression Model
1. 生成實質人均所得
```{r}
df1995$Rincome <- with(df1995, income/population/cpi)

```

2. 使用`ivreg()`得到係數。
```{r}
cig_ivreg2 <- ivreg(log(packs) ~ log(Rprice) + log(Rincome) | log(Rincome) + SalesTax, data = df1995)

coeftest(cig_ivreg2, vcov = vcovHC, type = "HC1")
```

## Check Instrument Validity
1. 重新整理 CigarettesSW Data，並取出1985及1995年的資料。
```{r}
CigarettesSW <- CigarettesSW %>%
    mutate(
      Rincome = income/population/cpi,
      cigtax = tax/cpi
    )

df1985 <- subset(CigarettesSW, year == 1985)
df1995 <- subset(CigarettesSW, year == 1995)
```

2. 生成對應的變數。
```{r}
# diff of packs
pack_diff <- log(df1995$packs) - log(df1985$packs)

# diff of real price
Rprice_diff <- log(df1995$Rprice) - log(df1985$Rprice)

# diff of income
Rincome_diff <- log(df1995$Rincome) - log(df1985$Rincome)

# diff of SalesTax
SalesTax_diff <- df1995$SalesTax - df1985$SalesTax

# diff of cigarettes tax
cigtax_diff <- df1995$cigtax - df1985$cigtax
```

3. 3種不同的IV估計：
（1） TSLS 只用 `SalesTax` 當 instrument。
```{r}
cig_ivreg_diff1 <- ivreg(pack_diff ~ Rprice_diff + 
                           Rincome_diff | Rincome_diff + SalesTax_diff)
```

（2） TSLS 只用 `cigtax` 當instrument。
```{r}
cig_ivreg_diff2 <- ivreg(pack_diff ~ Rprice_diff + Rincome_diff | 
                           Rincome_diff + cigtax_diff)
```

（3）TSLS 使用 `SalesTax` 和 `cigtax` 當instrument。
```{r}
cig_ivreg_diff3 <- ivreg(pack_diff ~ Rprice_diff + Rincome_diff |
                           Rincome_diff + SalesTax_diff + cigtax_diff)
```

4. 3種Model比較
```{r}
# gather robust standard errors in a list
rob_se <- list(sqrt(diag(vcovHC(cig_ivreg_diff1, type = "HC1"))),
          sqrt(diag(vcovHC(cig_ivreg_diff2, type = "HC1"))),
           sqrt(diag(vcovHC(cig_ivreg_diff3, type = "HC1"))))

# generate table
stargazer(cig_ivreg_diff1, cig_ivreg_diff2,cig_ivreg_diff3,
  header = FALSE, 
  type = "text",
  digits = 3, 
  column.labels = c("IV: salestax", "IV: cigtax", "IVs: salestax, cigtax"),
  dep.var.labels.include = FALSE,
  dep.var.caption = "Dependent Variable: 1985-1995 Difference in Log per Pack Price",
  se = rob_se)
```

5. F-test
```{r}
# first-stage regressions
relevance1 <- lm(Rprice_diff ~ SalesTax_diff + Rincome_diff)
relevance2 <- lm(Rprice_diff ~ cigtax_diff + Rincome_diff)
relevance3 <- lm(Rprice_diff ~ Rincome_diff + SalesTax_diff + cigtax_diff)

# check instrument relevance for model (1)
linearHypothesis(relevance1, 
             "SalesTax_diff = 0", 
             vcov = vcovHC, type = "HC1")

# check instrument relevance for model (2)
linearHypothesis(relevance2, 
             "cigtax_diff = 0", 
             vcov = vcovHC, type = "HC1")

# check instrument relevance for model (3)
linearHypothesis(relevance3, 
             c("SalesTax_diff = 0", "cigtax_diff = 0"), 
             vcov = vcovHC, type = "HC1")
```

6. J-test
```{r}
cig_iv_OR <- lm(residuals(cig_ivreg_diff3) ~ Rincome_diff + SalesTax_diff + cigtax_diff)

linearHypothesis(cig_iv_OR, 
                 c("SalesTax_diff = 0", "cigtax_diff = 0"), 
                 test = "Chisq")
# chisq 卡方檢定

```

